cardinalR: Generating interesting high-dimensional data structures

### 2025-10-06 paper-cardinalR.Rmd
Added Mobius application

The `gen_mobius()` function is a wrapper around `geozoo::mobius()`, designed to simplify the generation of a Möbius strip in three dimensions for use in high-dimensional diagnostic studies. The function returns a tibble with $n$ sampled points forming the surface of a Möbius strip.

<!-- The Möbius strip is a classical non-orientable surface, looping back on itself with a half-twist. Its construction is based on a parameterization with angle $\theta \sim U(0, 2\pi)$ (position along the loop) and width $w \sim U(-0.4, 0.4)$ (offset across the band). The Cartesian coordinates are -->

<!-- $$ -->
<!-- X_1 = \Big(1 + \tfrac{w}{2} \cos(\tfrac{\theta}{2})\Big) \cos(\theta), \quad -->
<!-- X_2 = \Big(1 + \tfrac{w}{2} \cos(\tfrac{\theta}{2})\Big) \sin(\theta), \quad -->
<!-- X_3 = \tfrac{w}{2}\sin(\tfrac{\theta}{2}), -->
<!-- $$ -->

<!-- mapping a two-dimensional band with a half-twist into $\mathbb{R}^3$ as a one-sided, non-orientable surface. -->

<!-- While `gen_mobius()` directly produces a 3-D structure, the package framework allows embedding this strip in higher-dimensional spaces by appending additional Gaussian noise variables. This enables the Möbius strip to be used in the same comparative setting as other high-dimensional synthetic structures. -->

```{r data-mobius, echo=TRUE}
mobius <- gen_mobius(n = 1000)
```

>>>>

The `gen_mobius()` function is a wrapper around `geozoo::mobius()`, designed to simplify the generation of a Möbius strip in three dimensions for use in high-dimensional diagnostic studies. The function returns a tibble with $n$ sampled points forming the surface of a Möbius strip.
e
```{r data-mobius, echo=TRUE}
mobius <- gen_mobius(n = 1000)
```

The Möbius strip structure can model twisted or cyclic surfaces in physics and engineering, such as conveyor belts, molecular structures, or optical systems with non-orientable geometries [@optica2023].
